### 2017-01-22 manuscript.Rmd
before possible computer crash

Here we extend the basic particle filtering (algorithm) model, in order to:

- provide the capability to model the sensory consequences of self-initiated actions
- provide the capability to run a Monte Carlo simulation using the same generative model as is used for sensory inference

## State-Space Model

@@

# An Investigation of Various Priors
Here, we identify the various forms of predictive processing in the context of real-time sensory inference using SMC
## Related to Filtering Algorithm
## Higher-level Priors

@@

## Model mis-specification
## Re-use of same generative model
This may lead to leakage, i.e. inadvertently incorporating sensory evidence

@@

@@

# General Discussion

# Summary and conclusions
# Motion Data

>>>>

For sensory inference of a passive disturbance, the algorithm can be run with fixed parameters. Here we extend the basic particle filtering (algorithm) model, in order to:

- __provide the capability to model the sensory consequences of self-initiated actions__ (i.e. predict/infer the consequences of one's own actions)
- provide the capability to run a Monte Carlo simulation using the same generative model as is used for sensory inference

## Generative Model
The generative model is a state-space model, which itself is a dynamic model consisting of latent (state variables) and observed (measured) variables.

@@

# An Investigation of Various Priors
Here, we identify the various forms of predictive processing in the context of real-time sensory inference using SMC
## Related to Filtering Algorithm
## Higher-level Priors
control input -> infer the consequences of one's own actions.

@@

## Model mis-specification
If an observer uses a strong higher level prior, i.e. the wrong direction, this means that the data may be completely mis-interpreted. (call this: the effect of inappropriate priors [@Schwabe:2008ho])

## Re-use of same generative model
This may lead to leakage, i.e. inadvertently incorporating sensory evidence

@@

## Summary
Interference may the result of either inappropriate priors, leading to a mis-specified filtering algorithm, or biased decision-making. We should be able to investigate which by applying cognitive process models that explain response times and choices.

@@

# General Discussion
## A comparison with previous models
Unfortunately, there aren't many, but see [@Hiatt:2004tv]

## Support for our model: Nigmatullina

## Neuronal implementation
[@Lopez:2012ek; @Lopez:2011cc]
[@Klingner:2016ia]
[@zuEulenburg:2012bh]

# Summary and conclusions

# Acknowledgements

# Motion Data
